---
title: "Curriculum Vitae"
description: "Positions, education, leadership, and service."
format:
  html: default
  typst:                          # the same source, typeset as a PDF (docs/cv.pdf)
    title: "Abhishek Bhattacharjee, PhD"
    subtitle: "Curriculum Vitae"
    template-partials:            # pencil on paper: the site's material, on the page
      - typst-template.typ
      - typst-show.typ
    font-paths: [fonts/ttf]
    toc: false
format-links: false
filters:
  - chalk                         # on paper, the CV's classes become the template's functions
knitr:
  opts_chunk:
    dev: "ragg_png"               # R's own png device wants X11 on this machine
---

::: {.content-visible when-format="html"}
Chennai, India ·
[Google Scholar](https://scholar.google.com/citations?user=9LJsXtMAAAAJ&hl=en) ·
[LinkedIn](https://www.linkedin.com/in/stat-absk/) ·
[PDF](cv.pdf)
:::

::: {.content-visible when-format="typst"}
Chennai, India · stat-absk.github.io · [Google Scholar](https://scholar.google.com/citations?user=9LJsXtMAAAAJ&hl=en) · [LinkedIn](https://www.linkedin.com/in/stat-absk/)
:::

## Profile

Biostatistics leader pairing hands-on industry development and FDA regulatory
experience across the drug-development lifecycle with a strong academic and
methodological foundation. Currently Senior Manager, Biostatistics at Pfizer
(Associate Director–equivalent) and a member of the Data Science & Analytics
India leadership team, leading a team of statisticians across global Oncology and
Inflammation & Immunology programs. Former FDA Oncology Center of Excellence
primary reviewer with hands-on NDA/BLA experience, product-labelling negotiation,
and pioneering use of real-world evidence and external-control cohorts.

::: {.content-visible when-format="typst"}
## Core competencies

Clinical development strategy · Regulatory interactions (FDA) · Oncology & I&I trial design · NDA / BLA / IND submissions · Endpoint & estimand strategy · Real-world evidence · Target trial emulation · Bayesian & adaptive designs · People leadership & mentoring · Cross-functional influence · Reproducible workflows · Scientific publication & speaking
:::

## Experience

```{r}
#| label: career-strip
#| echo: false
#| results: asis
source("R/theme_chalk.R")
roles <- tibble::tribble(
  ~role,                         ~where,                  ~kind,                 ~from,        ~to,          ~flip,
  "Statistician",                "Cytel",                 "Industry & practice", "2011-06-01", "2012-04-30", FALSE,
  "Graduate assistant",          "University of Florida", "University",          "2012-08-01", "2017-08-31", FALSE,
  "Assistant professor",         "Northern Colorado",     "University",          "2017-08-01", "2019-07-31", TRUE,
  "Biostatistician",             "Nemours",               "Industry & practice", "2019-08-01", "2020-01-31", TRUE,
  "Mathematical statistician",   "FDA",                   "Regulator",           "2020-02-01", "2022-04-30", FALSE,
  "Manager",                     "",                      "Industry & practice", "2022-05-01", "2024-05-31", FALSE,
  "Senior Manager",              "Pfizer",                "Industry & practice", "2024-06-01", as.character(Sys.Date()), FALSE
)
roles$from <- as.Date(roles$from); roles$to <- as.Date(roles$to)
kinds <- c("Industry & practice", "Regulator", "University")
roles$y    <- match(roles$kind, kinds)
roles$now  <- roles$to >= Sys.Date() - 1          # the one role to look at: the current one
# Labels sit above the bar (role) and below it (where); where two roles follow
# each other on a row, the second is flipped so nothing collides.
roles$role_y  <- roles$y + ifelse(roles$flip, -0.34, 0.3)
roles$where_y <- roles$y + ifelse(roles$flip, 0.3, -0.34)
# Data ink only: the bars, their names, a range-frame axis from the first day
# to today. The current role carries the accent; the rest sit in the second ink.
strip <- ggplot(roles) +
  geom_segment(aes(x = from, xend = to, y = y, yend = y, colour = now),
               linewidth = 2.6, lineend = "round", show.legend = FALSE) +
  geom_text(aes(x = from, y = role_y, label = role), hjust = 0, size = 3.3,
            colour = chalk_colours[["ink"]], family = "Atkinson Hyperlegible Next") +
  geom_text(aes(x = from, y = where_y, label = where), hjust = 0, size = 3,
            colour = chalk_colours[["ink3"]], family = "Atkinson Hyperlegible Next") +
  scale_colour_manual(values = c(`FALSE` = chalk_colours[["ink2"]], `TRUE` = chalk_colours[["accent"]])) +
  scale_x_date(breaks = as.Date(paste0(seq(2012, 2026, 2), "-01-01")), date_labels = "%Y",
               limits = c(min(roles$from), max(roles$to)), expand = c(0, 0)) +
  scale_y_continuous(breaks = 1:3, labels = kinds, expand = expansion(add = 0.65)) +
  coord_cartesian(clip = "off") +
  labs(x = NULL, y = NULL) +
  theme_chalk() +
  theme(plot.margin = margin(4, 48, 4, 0))        # room for the last label past the frame
chalk_inline(strip, width = 6.6, height = 2.3, name = "career-strip",
  summary ="Seven roles on one time axis from 2011 to now: Cytel in 2011, the University of Florida from 2012 to 2017, the University of Northern Colorado to 2019, Nemours in 2019, the FDA from 2020 to 2022, and Pfizer since 2022.")
```

::: {.cv-entry}
[Jun 2024 – present]{.cv-when}
[Senior Manager, Biostatistics]{.cv-what} — Pfizer Healthcare India Pvt. Ltd., Chennai, India

- Associate Director–equivalent statistical leader on the Data Science & Analytics
  India leadership team, shaping statistical strategy across global
  Inflammation & Immunology development programs.
- Lead and develop a team of statisticians — building talent, strengthening
  statistical capability, and fostering a culture of scientific excellence.
- Build enterprise capability in real-world evidence and target trial emulation,
  partnering with Statistics leadership to advance next-generation evidence generation.
- Advance modern quantitative methods across programs, including endpoint
  consolidation, real-time trial monitoring, and reproducible quantitative science.
:::

::: {.cv-entry}
[May 2022 – May 2024]{.cv-when}
[Manager, Biostatistics]{.cv-what} — Pfizer Healthcare India Pvt. Ltd., Chennai, India

- Trial-statistician leadership across Inflammation & Immunology programs spanning
  pediatric ulcerative colitis and inflammatory bowel disease, with medical-affairs
  support and priority programs in atopic dermatitis, asthma, and COPD — from study
  design through regulatory deliverables.
- Oncology statistical leadership on targeted-therapy programs across non-small cell
  lung cancer and melanoma, spanning protocol design, analysis planning, and
  submission-supporting deliverables.
:::

::: {.cv-entry}
[Feb 2020 – Apr 2022]{.cv-when}
[Mathematical Statistician (Primary Reviewer)]{.cv-what} — U.S. Food and Drug
Administration, Oncology Center of Excellence, Silver Spring, MD, USA

- Primary statistical reviewer for NDA, BLA, and IND submissions across multiple
  oncology indications, delivering independent assessments that informed regulatory
  decisions and product labelling.
- Reviewed applications spanning gastric and gastroesophageal cancers,
  cholangiocarcinoma, and additional solid-tumor indications, as well as an oncology
  biosimilar and a supportive-care (otoprotection) program.
- Led sponsor–agency interactions and labelling negotiations, translating statistical
  findings into clear regulatory positions.
- Contributed to one of the FDA's early evaluations of real-world evidence and
  external-control cohorts through review of a pediatric neuroblastoma program.
:::

::: {.cv-entry}
[Aug 2019 – Jan 2020]{.cv-when}
[Biostatistician]{.cv-what} — Nemours Children's Health System, Jacksonville, FL, USA

- Led end-to-end statistical strategy for investigator-initiated pediatric studies
  across multiple therapeutic areas — concept and design through analysis,
  interpretation, and publication.
:::

::: {.cv-entry}
[Aug 2017 – Jul 2019]{.cv-when}
[Assistant Professor of Statistics (tenure-track)]{.cv-what} — University of
Northern Colorado, Greeley, CO, USA

- Taught graduate and undergraduate statistics, mentored students, and led applied
  and methodological research.
- Served as statistical consultant on cross-disciplinary research collaborations
  across the university.
:::

::: {.cv-entry}
[Aug 2012 – Aug 2017]{.cv-when}
[Graduate Assistant & Instructor]{.cv-what} — University of Florida,
Department of Statistics, Gainesville, FL, USA

- Instructor, teaching assistant, and statistical consultant while completing PhD research.
:::

::: {.cv-entry}
[Jun 2011 – Apr 2012]{.cv-when}
[Statistician]{.cv-what} — Cytel Statistical Software & Services Pvt. Ltd., Pune, India

- Supported early-stage sponsor studies through statistical programming, analysis,
  and study-support activities.
:::

## Education

::: {.cv-entry}
[2012 – 2017]{.cv-when}
[PhD, Statistics]{.cv-what} — University of Florida
:::

::: {.cv-entry}
[2009 – 2011]{.cv-when}
[MSc, Statistics]{.cv-what} — University of Calcutta
:::

::: {.cv-entry}
[2006 – 2009]{.cv-when}
[BSc, Statistics]{.cv-what} — University of Calcutta
:::

::: {.cv-entry}
[2025]{.cv-when}
[Leadership Development Programme]{.cv-what} — IIM Ahmedabad (for Pfizer)
:::

## Professional leadership & scientific service

- Scientific Committee Member — International Indian Statistical Association (IISA)
- Council Member, Biostatistics Council — Indian Society for Clinical Research (ISCR)
- Mentor, Pfizer statistics internship program
- Biostatistics workshops — Loyola College and SSKM Hospital, Kolkata

## Selected presentations

- IISA Annual Conference — 2024, 2022
- Novartis Sankhya — 2023
- International Triennial Calcutta Symposium on Probability & Statistics — 2018, 2015
- ASA Joint Statistical Meetings (JSM) — 2017

## Research focus

Much of my recent work sits in two places: using **target trial emulation** to
bring observational data to bear on questions trials answer slowly or not at all,
and **endpoint and estimand strategy** — deciding what a trial should measure
before arguing about how to analyse it.

## Publications

{{< tally 15 >}} peer-reviewed journal articles · 315 citations (as of July 2026) ·
[Google Scholar](https://scholar.google.com/citations?user=9LJsXtMAAAAJ&hl=en)

```{r}
#| label: papers-by-year
#| echo: false
#| results: asis
source("R/theme_chalk.R")
papers <- data.frame(
  year  = c(2026, 2026, 2025, 2025, 2025, 2025, 2024, 2021, 2020, 2020, 2019, 2019, 2019, 2017, 2017),
  first = c(FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, FALSE, TRUE, FALSE, FALSE)
)
papers$n <- ave(papers$year, papers$year, FUN = seq_along)
# One dot per paper, stacked by year; the single first-authored paper is ringed
# in the accent. No axis line, no grid: the dots and four year labels are all.
dots <- ggplot(papers, aes(year, n)) +
  geom_point(colour = chalk_colours[["ink2"]], size = 2.2) +
  geom_point(data = subset(papers, first), shape = 1, size = 6, stroke = 1,
             colour = chalk_colours[["accent"]]) +
  scale_x_continuous(breaks = c(2017, 2020, 2023, 2026), limits = c(2016.5, 2026.5)) +
  scale_y_continuous(breaks = NULL, expand = expansion(add = c(0.8, 0.8))) +
  labs(x = NULL, y = NULL) +
  theme_chalk(base_size = 13) +
  theme(axis.line.x = element_blank(), plot.margin = margin(0, 0, 0, 0))
chalk_inline(dots, width = 2.2, height = 1.4, class = "figure-chalk margin-figure", name = "papers-by-year",
  summary = "Fifteen papers by year from 2017 to 2026, one dot each; the first-authored paper, in 2019, is circled.")
```

### 2026

1. Dubinsky MC, Cohen ER, Irving PM, … **Bhattacharjee A**, et al. Bowel urgency in
   ulcerative colitis is associated with clinical endpoints, health-related quality
   of life, and biomarkers: data from the etrasimod ELEVATE UC 52 trial.
   *Crohn's & Colitis 360*. 2026;otag072. [doi](https://doi.org/10.1093/crocol/otag072)

2. Makgoeng SB, Gamalo M, Russo LJ, Pradhan V, **Bhattacharjee A**, Bhosale N.
   Data-driven trial design: use of target trial emulation to evaluate eligibility
   criteria in asthma and COPD. *Frontiers in Medicine*. 2026;13:1863026. [doi](https://doi.org/10.3389/fmed.2026.1863026)

### 2025

3. Armuzzi A, Rubin DT, Schreiber S, … **Bhattacharjee A**, et al. Health-related
   quality of life outcomes with etrasimod treatment in patients with ulcerative
   colitis: a post hoc analysis of data from ELEVATE UC 52 and ELEVATE UC 12.
   *Inflammatory Bowel Diseases*. 2025;31(6):1583–1594. [doi](https://doi.org/10.1093/ibd/izae229)

4. Jairath V, Rubin DT, Verstockt B, … **Bhattacharjee A**, et al. The effect of
   etrasimod on fecal calprotectin and high-sensitivity C-reactive protein: results
   from the ELEVATE UC clinical program. *Inflammatory Bowel Diseases*.
   2025;31(4):923–934. [doi](https://doi.org/10.1093/ibd/izae111)

5. Magro F, Peyrin-Biroulet L, Sands BE, … **Bhattacharjee A**, et al. Endoscopic,
   histologic, and composite endpoints in patients with ulcerative colitis treated
   with etrasimod. *Clinical Gastroenterology and Hepatology*. 2025;23(2):341–350. [doi](https://doi.org/10.1016/j.cgh.2024.07.010)

6. Afzali A, Regueiro M, Yarur AJ, … **Bhattacharjee A**, et al. Concomitant use of
   etrasimod with opioids or antidepressants in patients with ulcerative colitis —
   a safety analysis. *United European Gastroenterology Journal*. 2025;13(5):719–727. [doi](https://doi.org/10.1002/ueg2.12745)

### 2024

7. Regueiro M, Siegmund B, Yarur AJ, … **Bhattacharjee A**, et al. Etrasimod for the
   treatment of ulcerative colitis: analysis of infection events from the ELEVATE UC
   clinical programme. *Journal of Crohn's and Colitis*. 2024;18(10):1596–1605. [doi](https://doi.org/10.1093/ecco-jcc/jjae060)

### 2021 and earlier

8. Imerci A, Rogers KJ, **Bhattacharjee A**, Bowen JR, Thacker MM. Risk factors for
   failure of Pavlik harness treatment in infants with dislocated hips evaluated by
   dynamic sonography. *Journal of Pediatric Orthopaedics*. 2021;41(6):e386–e391. [doi](https://doi.org/10.1097/bpo.0000000000001799)

9. Chatterjee N, Nair PKR, Nair VD, Viswanath S, **Bhattacharjee A**. Depth-wise
   distribution of soil-carbon stock in aggregate-sized fractions under
   shaded-perennial agroforestry systems in the Western Ghats of Karnataka, India.
   *Agroforestry Systems*. 2020;94(2):341–358. [doi](https://doi.org/10.1007/s10457-019-00399-z)

10. Alharash H, Hossain MJ, **Bhattacharjee A**, Levenbrown Y. Use of pulse contour
    technology for continuous blood pressure monitoring in pediatric patients.
    *Blood Pressure Monitoring*. 2020;25(5):278–284. [doi](https://doi.org/10.1097/mbp.0000000000000458)

11. Chatterjee N, Nair PKR, Nair VD, **Bhattacharjee A**, et al. Do coffee agroforestry
    systems always improve soil carbon stocks deeper in the soil? A case study from
    Turrialba, Costa Rica. *Forests*. 2019;11(1):49. [doi](https://doi.org/10.3390/f11010049)

12. Ying W, **Bhattacharjee A**, Wu SS. Effect of laser acupuncture on mitigating
    anxiety in acute stressed horses: a randomized, controlled study. *American
    Journal of Traditional Chinese Veterinary Medicine*. 2019;14(1).

13. **Bhattacharjee A**, Ghosh M. Bias-corrected empirical Bayes confidence intervals
    for the selected mean. *Communications in Statistics — Theory and Methods*.
    2019;48(3):583–595. [doi](https://doi.org/10.1080/03610926.2017.1417427)

14. Ahn H, Woods AJ, Kunik ME, … **Bhattacharjee A**, et al. Efficacy of transcranial
    direct current stimulation over primary motor cortex and contralateral
    supraorbital area on clinical pain severity and mobility performance in persons
    with knee osteoarthritis: a randomized, sham-controlled pilot study.
    *Brain Stimulation*. 2017;10(5):902–909. [doi](https://doi.org/10.1016/j.brs.2017.05.007)

15. Wu SS, Chen S, **Bhattacharjee A**, He Y. Collusion-resistant multi-matrix masking
    for privacy-preserving data collection. *2017 IEEE 3rd International Conference
    on Big Data Security on Cloud (BigDataSecurity)*. 2017:1–7. [doi](https://doi.org/10.1109/bigdatasecurity.2017.10)
